### 2016-07-01 store-consistency.tex
Edits to the note about parameterization.

>>>>

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality owing to the subtle differences in the semantics of isolation
levels among databases. For instance, Postgres's \iso{Repeatable Read}
isolation is stronger than ANSI SQL's or MySQL's in non-trivial ways.
Furthermore, the need for high availability on geo-replicated stores
has led to the development of of new isolation levels which are yet to
be standardized. For example, \emph{Parallel Snapshot
Isolation}~\cite{psi} was proposed in 2011, and \emph{Non-Monotonic
Snapshot Isolation}~\cite{nmsi} in 2013, both targeted for replicated
stores. As more commercial weakly consistent stores adopt variants of
transactions (like the \emph{lightweight transactions} of Cassandra),
it is reasonable to expect novel forms of isolation to be proposed.
While it is possible to carefully engineer a reasoning framework for
each combination of consistency and isolation, it leads to multiple
proof systems with no obvious to compare proofs.  Having a
parameterized semantics and proof framework built on this semantics
allows us to support these variants as distinct, yet comparable
instantiations, thus avoiding the need for semantics re-engineering
every time an application is retargeted to a new platform

%   A distinguishing feature of our framework is that it
%   is parameteric over different isolation and consistency
%   instantiations, whose properties can be encapsulated within the
%   trace invariant $\I$.  While it is true that most relational
%   databases implement standard ANSI SQL isolation levels similar to
%   the ones shown in Fig.~\ref{fig:ansi-isolation}, there is no clear
%   agreement on the exact semantics of these isolation levels on
%   various weakly-consistent stores.  Thus, what Oracle calls
%   serializable isolation is a slightly stronger variant of snapshot
%   isolation.  Having a parameterized semantics and proof framework
%   built on this semantics allows us to support these variants
%   without the need for semantics re-engineering every time an
%   application is retargeted to a new platform.

%   Moreover, the need for high availability on geo-replicated stores
%   is incentivizing the development of new isolation
%   levels. \emph{Parallel Snapshot Isolation}, for example, was
%   proposed in 2011, and \emph{Non-Monotonic Snapshot
%     Isolation}~\cite{...} in 2013, both for replicated
%   stores. Commercial eventually-consistent stores have only just
%   started adopting transactions (the first release of Cassandra with
%   support for multi-key transactions is slated for later this year),
%   and all indications are that we should expect to see new isolation
%   instantiations in the future.  Without parameterization, we would
%   need to carefully engineer a reasoning framework for each
%   isolation and consistency variant.  Clearly, each such framework
%   would be incomparable to one another. On the other hand, our
%   treatment allows us to accommodate the myriad of different
%   isolation and store-consistency instances without the need for
%   bespoke specialization.
